|

### 2024-01-01 JCGS_response_to_reviews/response_to_review_R1.Rmd

---
title: "Response to Reviews: JCGS-23-139.R1"
author: Weihao Li, Emi Tanaka, Dianne Cook, Susan VanderPlas
output: pdf_document
date: "`r Sys.Date()`"
bibliography: ../ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We thank the anonymous associate editor and reviewers for their careful reviews. What follows is our point-by-point response to reviewer comments.

Note that *the original reviewer comments are in italic* and our response is in normal text.

# Reviewer 1

*Good response.*

Thank you. (...)

# Reviewer 2

*I appreciate the effort provided by the authors for both my comments and the other reviewer’s comments. The revision is much improved. I have a few remaining comments.*

Thank you. (...)

*1. I still believe the paper is too long. Starting with Section 4, I believe the paper starts to become a little too cumbersome. I suggest the authors look for ways to condense down Sections 4 and 5 a bit as I think these are the biggest contributors to the length.*

*2. In the Figure 1 caption, clarify what is meant by the "at position $2^2 + 2$".*

*3. In the footnote on the bottom of page6, replace "didn't" and "it's" by "did not" and "it is", respectively.*

*4. In the last sentence of Section 2.2, the final segment "statistical and practical statistics" sounds awkward because "statistical" should be serving as an adjective to another word, and the segment as written makes it sound like it is also an adjective to "statistics". The authors might consider replacing "statistical" with "classic inference" as the paper is addressing the discrepancies between inferential results and what may be practically done.*

*5. Page 21 onward, there are many instances where the figure references did not compile correctly. These need to be corrected.*

### 2024-01-01 appendix.Rmd
reduce 2 pages

>>>>

# Additional details of experimental design

## Non-linearity

The non-linearity model used in the experiment includes a non-linear term $\boldsymbol{z}$ constructed using Hermite polynomials on random vector $\boldsymbol{x}$ formulated as

\begin{align*} \label{eq:nonlinearity-model}
\boldsymbol{y} &= \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{z} + \boldsymbol{\varepsilon},\\
\boldsymbol{x} &= g(\boldsymbol{x}_{raw}, 1), \\
\boldsymbol{z} &= g(\boldsymbol{z}_{raw}, 1), \\
\boldsymbol{z}_{raw} &= He_j(g(\boldsymbol{x}, 2)),
\end{align*}

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{x}_{raw}$, $\boldsymbol{z}_{raw}$ are vectors of size $n$, $\boldsymbol{1}_n$ is a vector of ones of size $n$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials [@hermite1864nouveau; originally by @de1820theorie], $\varepsilon \sim N(\boldsymbol{0}_n, \sigma^2\boldsymbol{I}_n)$, and $g(\boldsymbol{x}, k)$ is a scaling function to enforce the support of the random vector to be $[-k, k]^n$ defined as

```{=tex}
\begin{equation} \label{eq:scaling-function}
g(\boldsymbol{x}, k) = 2k\cdot\frac{\boldsymbol{x} - x_{min}\boldsymbol{1}_n}{x_{max} - x_{min}} - k, \quad \text{for} \quad k > 0. 
\end{equation}
```

\noindent where $\displaystyle x_{min} = \min_{i\in \{1, ..., n\}} x_i$, $\displaystyle x_{max} = \max_{i\in \{1, ..., n\}} x_i$ and $x_i$ is the $i$-th entry of $\boldsymbol{x}$. The function `hermite` from the R package `mpoly` [@mpoly] is used to simulate $\boldsymbol{z}_{raw}$ to generate Hermite polynomials.

The null regression model used to fit the realizations generated by the above model is formulated as

```{=tex}
\begin{equation} \label{eq:null-model}
\boldsymbol{y} = \beta_0\boldsymbol{1}_n + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}
```
\noindent where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$. Here $\boldsymbol{z}$ is a higher order term of $\boldsymbol{x}$ and leaving it out in the null regression results in model misspecification.

## Heteroskedasticity

The heteroskedasticity model used in the experiment is formulated as

\begin{align*} \label{eq:heter-model}
\boldsymbol{y} &= \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{\varepsilon},\\
\boldsymbol{x} &= g(\boldsymbol{x}_{raw}, 1),\\
\boldsymbol{\varepsilon} &\sim N(\boldsymbol{0}_n, \boldsymbol{1}_n + (2 - |a|)(\boldsymbol{x} - a\boldsymbol{1}_n)'(\boldsymbol{x} - a\boldsymbol{1}_n) b \boldsymbol{I}_n), 
\end{align*}

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$ are vectors of size $n$ and $g(.)$ is the scaling function defined in Equation \ref{eq:scaling-function}. The null regression model used to fit the realizations generated by the above model is formulated exactly the same as Equation \ref{eq:null-model}.

For $b \neq 0$, the variance-covariance matrix of the error term $\boldsymbol{\varepsilon}$ is correlated with the predictor $\boldsymbol{x}$, which will lead to the presence of heteroskedasticity.

Since $\text{supp}(X) = [-1, 1]$, choosing $a$ to be $-1$, $0$ and $1$ can generate "left-triangle", "butterfly" and "right-triangle" shapes. The term $(2 - |a|)$ maintains the magnitude of residuals across different values of $a$.

## Controlling the signal strength

The three parameters $n$, $\sigma$ and $b$ are important for controlling the strength of the signal to generate lineups with a variety difficulty levels. This will ensure that  estimated power curves will be smooth and continuous, and that participants are allocated a set of lineups with a range of difficulty.

Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ are used in data collection periods I and II respectively. A large value of $\sigma$ will increase the variation of the error of the non-linearity model and decrease the visibility of the visual pattern. 
The parameter $b$ controls the variation in the standard deviation of the error across the support of the predictor. A larger value of $b$ generates a larger ratio between it's smallest and highest values, making the visual pattern more obvious. 
The sample size $n$ sharpens (or blurs) a pattern when it is larger (or smaller).

<!-- Figures \ref{fig:different-sigma}, \ref{fig:different-b} and \ref{fig:different-n} demonstrate the impact of these parameters on signal strength.  -->

### Lineup allocation to participants

From Table \ref{tab:model-factor-table} it can be computed that there are a total of $4 \times 4 \times 3 \times 4 = 192$ and $3 \times 5 \times 3 \times 4 = 180$ combinations of parameter values for the non-linearity model and heteroskedasticity models respectively. Three replications for each combination results in $192 \times 3 = 576$ and $180 \times 3 = 540$ lineups, respectively.

Each lineup needs to be evaluated by at least five participants. From previous work, and additional pilot studies for this experiment, we decided to record evaluations from 20 lineups for each participant. Two of the 20 lineups with clear visual patterns were used as attention checks, to ensure quality data. Thus, $576 \times 5 / (20-2) = 160$ and $540 \times 5 / (20-2) = 150$ participants were needed to cover the experimental design for the data collection periods I and II, respectively. The factor levels and range of difficulty was assigned relatively equally among participants. The Appendix contains graphical summaries of these assignments for each subject.

Data collection period III was primarily to obtain Rorschach lineup evaluations to estimate $\alpha$ (see Section A.1 in the Appendix), and also to obtain additional evaluations of lineups made with uniform fitted value distribution to ensure consistency in the results. To construct a Rorschach lineup, the data is generated from a model with zero effect size, while the null data are generated using the same simulation method discussed in Section \ref{visual-test-procedure-based-on-lineups}. This procedure differs from that of the canonical Rorschach lineup, where all 20 plots are generated directly from the null model, so the method suggested in @vanderplas2021statistical for typical lineups containing a data plot is used to estimate $\alpha$. (The Appendix contains a sensitivity analysis on the effect of uncertainty in the estimation of $\alpha$.) The $3 \times 4 = 12$ treatment levels of the common factors, replicated three times results in 36 lineups. And 6 more evaluations on the 279 lineups with uniform fitted value distribution, results in at least $(36 \times 20 + 279 \times 3 \times 6) / (20-2) = 133$ participants needed.

### Collecting results

Participants for all three data collection periods were recruited from the Prolific crowd-sourcing platform [@palan2018prolific]. Pre-screening procedures were applied during the recruitment: participants were required to be fluent in English, with $98\%$ minimum approval rate and at least 10 submissions in other studies.

In each lineup evaluation, the participant was asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots are from others. If there is no noticeable difference between plots in a lineup, participants had the option to select zero plots without the need to provide a reason. During the process of recording the responses, a zero selection was considered to be equivalent to selecting all 20 plots. No participant was shown the same lineup twice. Information about preferred pronouns, age group, education, and previous experience in visual experiments were also collected. A participant's submission was only included in the analysis if the data plot is identified for at least one attention check.

### 2024-01-01 paper.Rmd
reduce 2 pages

Our experiment was conducted over three data collection periods to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. Two types of departures, non-linearity and heteroskedasticity, were collected during data collection periods I and II. The data collection period III was designed primarily to measure human responses to null lineups so that the visual $p$-values can be estimated. Additional lineups for both non-linearity and heteroskedasticity, using uniform fitted value distributions, were included for additional data, and to avoid participant frustration of too many difficult tasks. Overall, we collected `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` participants throughout three data collection periods.

@@

### Non-linearity

@@

\begin{align*} \label{eq:nonlinearity-model}
\boldsymbol{y} &= \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{z} + \boldsymbol{\varepsilon},\\
\boldsymbol{x} &= g(\boldsymbol{x}_{raw}, 1), \\
\boldsymbol{z} &= g(\boldsymbol{z}_{raw}, 1), \\
\boldsymbol{z}_{raw} &= He_j(g(\boldsymbol{x}, 2)),
\end{align*}

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{x}_{raw}$, $\boldsymbol{z}_{raw}$ are vectors of size $n$, $\boldsymbol{1}_n$ is a vector of ones of size $n$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials [@hermite1864nouveau; originally by @de1820theorie], $\varepsilon \sim N(\boldsymbol{0}_n, \sigma^2\boldsymbol{I}_n)$, and $g(\boldsymbol{x}, k)$ is a scaling function to enforce the support of the random vector to be $[-k, k]^n$ defined as

```{=tex}
\begin{equation} \label{eq:scaling-function}
g(\boldsymbol{x}, k) = 2k\cdot\frac{\boldsymbol{x} - x_{min}\boldsymbol{1}_n}{x_{max} - x_{min}} - k, \quad \text{for} \quad k > 0. 
\end{equation}
```

\noindent where $\displaystyle x_{min} = \min_{i\in \{1, ..., n\}} x_i$, $\displaystyle x_{max} = \max_{i\in \{1, ..., n\}} x_i$ and $x_i$ is the $i$-th entry of $\boldsymbol{x}$. The function `hermite` from the R package `mpoly` [@mpoly] is used to  simulate $\boldsymbol{z}_{raw}$ to generate Hermite polynomials.

The null regression model used to fit the realizations generated by the above model is formulated as

```{=tex}
\begin{equation} \label{eq:null-model}
\boldsymbol{y} = \beta_0\boldsymbol{1}_n + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}
```
\noindent where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$. Here $\boldsymbol{z}$ is a higher order term of $\boldsymbol{x}$ and leaving it out in the null regression results in model misspecification.

@@

Visual patterns of non-linearity are simulated using four different orders of probabilist's Hermite polynomials ($j = 2, 3, 6, 18$). The values of $j$ were chosen so that distinct shapes of non-linearity were included in the residual plot. These include "U", "S", "M" and "triple-U" shape as shown in Figure \ref{fig:different-shape-of-herimite}. A greater value of $j$ will result in a curve with more turning points. It is expected that the "U" shape will be the easiest to detect, and as the shape gets more complex it will be harder to perceive in a scatterplot, particularly when there is noise. Figure \ref{fig:different-sigma} shows the "U" shape for different amounts of noise ($\sigma$).

### Heteroskedasticity

Data collection period II was designed to study the ability of participants to detect the heteroskedasticity under a simple linear regression model setting:

\begin{align*} \label{eq:heter-model}
\boldsymbol{y} &= \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{\varepsilon},\\
\boldsymbol{x} &= g(\boldsymbol{x}_{raw}, 1),\\
\boldsymbol{\varepsilon} &\sim N(\boldsymbol{0}_n, \boldsymbol{1}_n + (2 - |a|)(\boldsymbol{x} - a\boldsymbol{1}_n)'(\boldsymbol{x} - a\boldsymbol{1}_n) b \boldsymbol{I}_n), 
\end{align*}

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$ are vectors of size $n$ and $g(.)$ is the scaling function defined in Equation \ref{eq:scaling-function}. The null regression model used to fit the realizations generated by the above model is formulated exactly the same as Equation \ref{eq:null-model}.

For $b \neq 0$, the variance-covariance matrix of the error term $\boldsymbol{\varepsilon}$ is correlated with the predictor $\boldsymbol{x}$, which will lead to the presence of heteroskedasticity. Visual patterns of heteroskedasticity are simulated using three different shapes ($a$ = -1, 0, 1).

Since $\text{supp}(X) = [-1, 1]$, choosing $a$ to be $-1$, $0$ and $1$ can generate "left-triangle", "butterfly" and "right-triangle" shapes as displayed in Figure \ref{fig:different-shape-of-heter}. The term $(2 - |a|)$ maintains the magnitude of residuals across different values of $a$. Figure \ref{fig:different-b} shows the butterfly shape as the ratio parameter ($b$) is changed.

@@

```{r different-b, fig.pos="!h", fig.height = 2, fig.cap = "Five different values of $b$ are used in heteroskedasticity simulation to control the strength of the signal. Larger values of $b$ yield a bigger difference in variation, and stus stronger heteroskedasticity signal."}

@@

Fitted values are a function of the independent variables, and the distribution of the observed values affects the distribution of the fitted values. In the best case scenario the fitted values will have a uniform distribution, which means that there is even coverage of possible observed values across all of the predictors. This is not always present in the collected data. Sometimes the fitted values are discrete because one or more predictors were measured discretely.  It is also common to see a skewed distribution of fitted values if one or more of the predictors has a skewed distribution. This latter problem is usually corrected before modelling, using a variable transformation. Our simulation assess this by using four different distributions to represent fitted values, constructed by different sampling of the raw predictor $X_{raw}$:

- uniform, $U(-1, 1)$, 
- normal, $N(0, 0.3^2)$, 
- skewed, $\text{lognormal}(0, 0.6^2)/3$, and 
- discrete, $U\{1, 5\}$.

\noindent Figure \ref{fig:different-dist} shows the non-linear pattern, a "U" shape, with the different fitted value distributions. We would expect that structure in residual plots would be easier to perceive when the fitted values are uniformly distributed.

@@

### Controlling the signal strength

The three parameters $n$, $\sigma$ and $b$ are important for controlling the strength of the signal to generate lineups with a variety difficulty levels. This will ensure that  estimated power curves will be smooth and continuous, and that participants are allocated a set of lineups with a range of difficulty.

Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ are used in data collection periods I and II respectively. A large value of $\sigma$ will increase the variation of the error of the non-linearity model and decrease the visibility of the visual pattern. 
The parameter $b$ controls the variation in the standard deviation of the error across the support of the predictor. A larger value of $b$ generates a larger ratio between it's smallest and highest values, making the visual pattern more obvious. 
The sample size $n$ sharpens (or blurs) a pattern when it is larger (or smaller). Figures \ref{fig:different-sigma}, \ref{fig:different-b} and \ref{fig:different-n} demonstrate the impact of these parameters on signal strength.

## Experimental setup

@@

### Effect size

@@

For the non-linearity model, the key items defining effect size are sample size ($n$) and variance of the error term ($\sigma^2$), and so effect size would be roughly calculated as $\sqrt{n}/{\sigma}$. As sample size increases the effect size would increase, but as variance increases the effect size decreases. However, it is not clear how the additional parameter for the model polynomial order, $k$, should be incorporated. Intuitively, the large $k$ means more complex pattern, which likely means effect size would decrease. For the purposes of our calculations we have chosen to use an approach based on Kullback-Leibler divergence [@kullback1951information], coupled with simulation. This formulation defines effect size to be:

@@

### Lineup allocation to participants

From Table \ref{tab:model-factor-table} it can be computed that there are a total of $4 \times 4 \times 3 \times 4 = 192$ and $3 \times 5 \times 3 \times 4 = 180$ combinations of parameter values for the non-linearity model and heteroskedasticity models respectively. Three replications for each combination results in $192 \times 3 = 576$ and $180 \times 3 = 540$ lineups, respectively.

Each lineup needs to be evaluated by at least five participants. From previous work, and additional pilot studies for this experiment, we decided to record evaluations from 20 lineups for each participant. Two of the 20 lineups with clear visual patterns were used as attention checks, to ensure quality data. Thus, $576 \times 5 / (20-2) = 160$ and $540 \times 5 / (20-2) = 150$ participants were needed to cover the experimental design for the data collection periods I and II, respectively. The factor levels and range of difficulty was assigned relatively equally among participants. The Appendix contains graphical summaries of these assignments for each subject.

Data collection period III was primarily to obtain Rorschach lineup evaluations to estimate $\alpha$ (see Section A.1 in the Appendix), and also to obtain additional evaluations of lineups made with uniform fitted value distribution to ensure consistency in the results. To construct a Rorschach lineup, the data is generated from a model with zero effect size, while the null data are generated using the same simulation method discussed in Section \ref{visual-test-procedure-based-on-lineups}. This procedure differs from that of the canonical Rorschach lineup, where all 20 plots are generated directly from the null model, so the method suggested in @vanderplas2021statistical for typical lineups containing a data plot is used to estimate $\alpha$. (The Appendix contains a sensitivity analysis on the effect of uncertainty in the estimation of $\alpha$.) The $3 \times 4 = 12$ treatment levels of the common factors, replicated three times results in 36 lineups. And 6 more evaluations on the 279 lineups with uniform fitted value distribution, results in at least $(36 \times 20 + 279 \times 3 \times 6) / (20-2) = 133$ participants needed.

### Collecting results

Participants for all three data collection periods were recruited from the Prolific crowd-sourcing platform [@palan2018prolific]. Pre-screening procedures were applied during the recruitment: participants were required to be fluent in English, with $98\%$ minimum approval rate and at least 10 submissions in other studies.

During the experiment, every participant is presented with a block of 20 lineups. A lineup consists of a randomly placed data plot and 19 null plots, which are all residual plots drawn with raw residuals on the y-axis and fitted values on the x-axis. An additional horizontal red line is added at $y = 0$ as a visual reference. The data in the data plot is simulated from one of two models described in Section \ref{simulating-departures-from-good-residuals}, while the data of the remaining 19 null plots are generated by the residual rotation technique discussed in Section \ref{visual-test-procedure-based-on-lineups}.

>>>>

Our experiment was conducted over three data collection periods to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. Two types of departures, non-linearity and heteroskedasticity, were collected during data collection periods I and II. The data collection period III was designed primarily to measure human responses to null lineups so that the visual $p$-values can be estimated. Additional lineups for both non-linearity and heteroskedasticity, using uniform fitted value distributions, were included for additional data, and to avoid participant frustration of too many difficult tasks.

During the experiment, every participant recruited from the Prolific crowd-sourcing platform [@palan2018prolific] is presented with a block of 20 lineups. A lineup consists of a randomly placed data plot and 19 null plots, which are all residual plots drawn with raw residuals on the y-axis and fitted values on the x-axis. An additional horizontal red line is added at $y = 0$ as a visual reference. The data in the data plot is simulated from one of two models described in Section \ref{simulating-departures-from-good-residuals}, while the data of the remaining 19 null plots are generated by the residual rotation technique discussed in Section \ref{visual-test-procedure-based-on-lineups}.

Overall, we collected `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` participants throughout three data collection periods.

@@

### Non-linearity and Heteroskedasticity

@@

$$ \boldsymbol{y} = \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{z} + \boldsymbol{\varepsilon},~\boldsymbol{\varepsilon} \sim N(\boldsymbol{0}_n, \sigma^2\boldsymbol{I}_n)$$

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{z}$ are vectors of size $n$, $\boldsymbol{1}_n$ is a vector of ones of size $n$, $\boldsymbol{z} \propto He_j(\boldsymbol{x})$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials [@hermite1864nouveau; originally by @de1820theorie].

To fit a misspecified model, the $\boldsymbol{z}$ term, which is a higher order term of $\boldsymbol{x}$, was omitted from the null regression formula

\begin{equation} \label{eq:null-model}
\boldsymbol{y} = \beta_0\boldsymbol{1}_n + \beta_1 \boldsymbol{x} + \boldsymbol{u},~ \boldsymbol{u} \sim N(\boldsymbol{0}_n, \sigma^2\boldsymbol{I}_n).
\end{equation}

Four different values of $j = 2, 3, 6, 18$ were chosen so that distinct shapes of non-linearity were included in the residual plot. These include "U", "S", "M" and "triple-U" shape as shown in Figure \ref{fig:different-shape-of-herimite}. A greater value of $j$ will result in a curve with more turning points. It is expected that the "U" shape will be the easiest to detect, and as the shape gets more complex it will be harder to perceive in a scatterplot, particularly when there is noise. Figure \ref{fig:different-sigma} shows the "U" shape for different amounts of noise ($\sigma$).

Data collection period II was similar to Data collection I but focuses on heteroskedasticity visual patterns formulated as

$$\boldsymbol{y} = \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{\varepsilon},~\boldsymbol{\varepsilon} \sim N(\boldsymbol{0}_n, \boldsymbol{1}_n + (2 - |a|)(\boldsymbol{x} - a\boldsymbol{1}_n)'(\boldsymbol{x} - a\boldsymbol{1}_n) b \boldsymbol{I}_n),$$
\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$ are vectors of size $n$.

The null regression model used to fit the realizations generated by the above model is formulated exactly the same as Equation \ref{eq:null-model}. For $b \neq 0$, the variance-covariance matrix of the error term $\boldsymbol{\varepsilon}$ is correlated with the predictor $\boldsymbol{x}$, which will lead to the presence of heteroskedasticity.

Visual patterns of heteroskedasticity are simulated using three different shapes ($a$ = -1, 0, 1) including "left-triangle", "butterfly" and "right-triangle" shapes as displayed in Figure \ref{fig:different-shape-of-heter}. Figure \ref{fig:different-b} shows the butterfly shape as the ratio parameter ($b$) is changed.

More details about the design of the data generating process are provided in the Appendix.

@@

@@

```{r different-b, fig.pos="!h", fig.height = 2, fig.cap = "Five different values of $b$ are used in heteroskedasticity simulation to control the strength of the signal. Larger values of $b$ yield a bigger difference in variation, and thus stronger heteroskedasticity signal."}

@@

Fitted values are a function of the independent variables, and the distribution of the observed values affects the distribution of the fitted values. In the best case scenario the fitted values will have a uniform distribution, which means that there is even coverage of possible observed values across all of the predictors. This is not always present in the collected data. Sometimes the fitted values are discrete because one or more predictors were measured discretely.  It is also common to see a skewed distribution of fitted values if one or more of the predictors has a skewed distribution. This latter problem is usually corrected before modelling, using a variable transformation. Our simulation assess this by using four different distributions to represent fitted values, constructed by different sampling of the raw predictor $X_{raw}$, namely, uniform ($U(-1, 1)$), normal ($N(0, 0.3^2)$), skewed ($\text{lognormal}(0, 0.6^2)/3$) and discrete ($U\{1, 5\}$).

Figure \ref{fig:different-dist} shows the non-linear pattern, a "U" shape, with the different fitted value distributions. We would expect that structure in residual plots would be easier to perceive when the fitted values are uniformly distributed.

@@

## Effect size

@@

@@

For the non-linearity model, the key items defining effect size are sample size ($n$) and variance of the error term ($\sigma^2$), and so effect size would be roughly calculated as $\sqrt{n}/{\sigma}$. As sample size increases the effect size would increase, but as variance increases the effect size decreases. However, it is not clear how the additional parameter for the model polynomial order, $j$, should be incorporated. Intuitively, the large $j$ means more complex pattern, which likely means effect size would decrease. For the purposes of our calculations we have chosen to use an approach based on Kullback-Leibler divergence [@kullback1951information], coupled with simulation. This formulation defines effect size to be:

@@
